Predictive modeling with cross validation

### 2017-08-24 model fitting/cross_validation.Rmd
more model fitting

# adding in spline on newline_ratio
model_spline3 <- coxph(Surv(time_until_answer, answered) ~ new_category + as.factor(new_user) + contain_unanswered + contain_answered + title_questionmark + sqrt(avg_tag_score) + text_all_lower + update + prior_effort + ampm + weekday + pspline(newline_ratio, df = 0, method = "AIC"), data = train1)
summary(model_spline3)
AIC(model_spline3, k = 2) # 64915.6
```

@@

@@

```{r}
allspline_avg <- get_avgmetrics(allsplines)
splinedev_avg <- get_avgmetrics(splinedev)
splinetext_avg <- get_avgmetrics(splinetext)
splinetag_avg <- get_avgmetrics(splinetag)
splinenew_avg <- get_avgmetrics(splinenew)
nospline_avg <- get_avgmetrics(nospline)
devtext_avg <- get_avgmetrics(devtext)
sqrtdev_avg <- get_avgmetrics(sqrtdev)
sqrttext_avg <- get_avgmetrics(sqrttext)

allspline_avg; splinedev_avg; splinetext_avg; splinetag_avg; splinenew_avg; nospline_avg; devtext_avg; sqrtdev_avg; sqrttext_avg
```

@@

list <- list(allsplines, splinedev, splinetext, splinetag, splinenew, nospline, devtext, sqrtdev, sqrttext)
names <- c("allsplines", "splinedev", "splinetext", "splinetag", "splinenew", "nospline", "devtext", "sqrtdev", "sqrttext") # change this to avoid hard coding

l_diff <- purrr::map(list, ~get_avgdiff(.))
df_diff <- plyr::ldply(purrr::map(1:length(l_diff), ~data.frame(as.list(l_diff[[.]]))), data.frame)
rownames(df_diff) <- names
df_diff

#least amount of average change found in model with only the spline on newline_ratio 
```

>>>>

# spline = avg_tag_length + device_length
model_spline3 <- coxph(Surv(time_until_answer, answered) ~ new_category + as.factor(new_user) + contain_unanswered + contain_answered + title_questionmark + sqrt(avg_tag_score) + text_all_lower + update + prior_effort + ampm + weekday + pspline(device_length, df = 0, method = "AIC") + pspline(avg_tag_length, df = 0, method = "AIC"), data = train1)
summary(model_spline3)
AIC(model_spline3, k = 2) # 64865.95

# adding in spline on newline_ratio
model_spline4 <- coxph(Surv(time_until_answer, answered) ~ new_category + as.factor(new_user) + contain_unanswered + contain_answered + title_questionmark + sqrt(avg_tag_score) + text_all_lower + update + prior_effort + ampm + weekday + pspline(newline_ratio, df = 0, method = "AIC"), data = train1)
summary(model_spline3)
AIC(model_spline4, k = 2) # 64915.6

# log10(text_length), spline = avg_tag_length + device_length
model_spline5 <- coxph(Surv(time_until_answer, answered) ~ new_category + as.factor(new_user) + contain_unanswered + contain_answered + title_questionmark + sqrt(avg_tag_score) + text_all_lower + update + prior_effort + ampm + weekday + log10(text_length) + sqrt(newline_ratio) + pspline(device_length, df = 0, method = "AIC") + pspline(avg_tag_length, df = 0, method = "AIC"), data = train1)
AIC(model_spline5, k = 2) # 64865.73

# log10(text_length), sqrt(newline_ratio), spline = avg_tag_length + device_length
model_spline5 <- coxph(Surv(time_until_answer, answered) ~ new_category + as.factor(new_user) + contain_unanswered + contain_answered + title_questionmark + sqrt(avg_tag_score) + text_all_lower + update + prior_effort + ampm + weekday + log10(text_length) + sqrt(newline_ratio) + pspline(device_length, df = 0, method = "AIC") + pspline(avg_tag_length, df = 0, method = "AIC"), data = train1)
AIC(model_spline5, k = 2) # 64864.73

# title_beginwh*title_questionmark, log10(text_length), sqrt(newline_ratio), spline = avg_tag_length + device_length
model_spline5 <- coxph(Surv(time_until_answer, answered) ~ new_category + as.factor(new_user) + contain_unanswered + contain_answered + title_questionmark + sqrt(avg_tag_score) + text_all_lower + update + prior_effort + ampm + weekday + log10(text_length) + sqrt(newline_ratio) + pspline(device_length, df = 0, method = "AIC") + pspline(avg_tag_length, df = 0, method = "AIC") + title_beginwh + title_questionmark*title_beginwh, data = train1)
AIC(model_spline5, k = 2) # 64858.68
```

@@

##### log10(text_length) + sqrt(newline_ratio) + splines: device_length, avg_tag_length + interaction between titlebeginwh*title_questionmark
```{r}
vars1 <- "new_category + as.factor(new_user) + contain_unanswered + contain_answered + title_questionmark + sqrt(avg_tag_score) + text_all_lower + update + prior_effort + ampm + weekday + log10(text_length) + sqrt(newline_ratio) + pspline(device_length, df = 0, method = 'AIC') + pspline(avg_tag_length, df = 0, method = 'AIC') + title_beginwh + title_questionmark*title_beginwh"

lots <- purrr::map2(trains, tests, ~crossval(vars1, .x, .y))
lots
```

@@

```{r}
# turn avg_list into a data frame with rownames???
list <- list(allsplines, splinedev, splinetext, splinetag, splinenew, nospline, devtext, sqrtdev, sqrttext, lots)
avg_list <- purrr::map(list, ~get_avgmetrics(.))
avg_list
```

@@

# find a way to put rownames on df_diff in a reproducible way 
l_diff <- purrr::map(list, ~get_avgdiff(.))
df_diff <- plyr::ldply(purrr::map(1:length(l_diff), ~data.frame(as.list(l_diff[[.]]))))
df_diff
#least amount of average change found in model with only the spline on newline_ratio 
```

```{r}
newline_text <- "new_category + as.factor(new_user) + contain_unanswered + contain_answered + title_questionmark + sqrt(avg_tag_score) + text_all_lower + update + prior_effort + ampm + weekday + log10(text_length) + pspline(newline_ratio, df = 0, method = 'AIC')"

sqrtdev <- purrr::map2(trains, tests, ~crossval(newline_text, .x, .y))
sqrtdev
```
